### 2022-07-12 about/vita.tex
Added thesis

\reportcount=4
\pubbegin R
\repitem Finding regularity in Tlingit verb prefixes. Semester project report, McGill University
(Montr\'eal, Qu\'ebec, April 2021), 7 pp.
\repitem Grid-building algorithms on manifolds. Summer research report, McGill University (Montr\'eal, Qu\'ebec,
August 2020), 10 pp.
\repitem Typechecking proof scripts: making interactive proof assistants robust.
Honours project report, McGill University (Montr\'eal, Qu\'ebec, December 2019), 10 pp.
\repitem The OPythn programming language. Software project report, Charles University (Prague,
Czech Republic, June 2019), 10 pp.

@@

\leftright{\bf Mentor}{\bf January 2021 -- present}
\leftright{\bf Department of Mathematics and Statistics, McGill University}{\sl Montr\'eal, QC, Canada}
\smallskip
Meet with two undergraduate students as part of the Directed Reading Program
on a weekly basis to give them an introduction to research-level
mathematics in a casual setting. Focused on topics in extremal combinatorics related to the increasing
triples problem.
\medbreak

>>>>

\reportcount=5
\pubbegin R
\repitem Structural properties of conditional Galton--Watson trees. M.Sc.~thesis, McGill University
(Montr\'eal, Qu\'ebec, August 2022), $\hbox{\rm vi} + 75$~pp.
\repitem Finding regularity in Tlingit verb prefixes. Semester project report, McGill University
(Montr\'eal, Qu\'ebec, April 2021), 7 pp.
\repitem Grid-building algorithms on manifolds. Summer research report, McGill University (Montr\'eal, Qu\'ebec,
August 2020), 10 pp.
\repitem Typechecking proof scripts: making interactive proof assistants robust.
Honours project report, McGill University (Montr\'eal, Qu\'ebec, December 2019), 10 pp.
\repitem The OPythn programming language. Software project report, Charles University (Prague,
Czech Republic, June 2019), 10 pp.

@@

\starleftright{\bf Visiting teaching assistant}{\bf July 2022}
\leftright{\bf Bocconi University}{\sl Como, CO, Italy}
\smallskip
Teaching assistant for a two-week summer school on random structures and combinatorial statistics,
which was
organised by Bocconi University in collaboration with Oxford University
and Imperial College London. Led problem sessions in the afternoons, with
around forty graduate-level students were in attendance.
\medbreak

\leftright{\bf Mentor}{\bf January -- April 2022}
\leftright{\bf Department of Mathematics and Statistics, McGill University}{\sl Montr\'eal, QC, Canada}
\smallskip
Meet with two undergraduate students as part of the Directed Reading Program
on a weekly basis to give them an introduction to research-level
mathematics in a casual setting. Focused on topics in extremal combinatorics related to the increasing
triples problem, as well as topics related to Khovanskii's theorem.
\medbreak
